### 2023-10-17 README.Rmd
Added scoreplot and plotmultflags to arguments for do_MSE
added poplevelplots for catch and cpue to output

>>>>

* 2023-10-17 aMSE 0.1.13 added poplevelplot() plots to the output. So far this includes catches and cpue. Population level plots can give insight into the effectiveness of the fleet dynamics and whether each population is being exploited.

* 2023-08-01 aMSE 0.1.10 Added scoreplots and plotmultflags into the arguments for do_MSE rather than requiring the functions be called plotfinalscores() and plotmultandflags(), so any name can be given to them.
